Information is Not Communicated Uniformly: Evidence from Spoken and Written Corpora

### 2019-01-29 cogsci/position-info.Rmd
cogsci edits

abstract: >
    We provide evidence against the popular Uniform Information Density hypothesis (Levy & Jaeger, 2007) which proposes that information is transmitted at a constant rate close to channel capacity in human communication. Using a method based on the original Genzel & Charniak (2002) entropy measure, we construct a word-level model for entropy applicable to both spoken and written corpora. We apply this model to corpora from Wikipedia in well over a hundred languages. We find that not only is the Uniform Information Density hypothesis prediction wrong, but also that the by-word entropy distribution of a language is related to the typological features of the language. We use this evidence to suggest that people do not communicate information at a uniform rate, but that information distribution varies from language to language based on phonogical, morphological and syntactic features.

@@

@@

**Evidence for UID here. Maybe see if you can present this work at a slightly higher level**
Their evidence concerns the use or lack of use of “that”-complementizers in introducing English relative clauses. When the word preceding the relative clause or the initial word of the relative clause has high information content, then the authors argue that speakers are more likely to use the complementizer. The authors use adult-adult conversations from the Penn Treebank corpus.

UID has been applied broadly over the past decade, to determining whether linguistic alignment takes place [@jaeger2013], Zipfian word length distributions [@piantadosi2011], communication efficiency [@mahowald2013], dialogue and turn-taking [@xu2018] and the significance of ambiguity in language [@piantadosi2012], among other research.

**Evidence against UID here. Again, can you present this at a higher level?**
However, other recent work has contradicted the UID hypothesis. @zhan2018 study Mandarin Chinese classifier use for specific and general Mandarin classifiers. Specific classifiers are specific to certain nouns, and UID would predict that specific classifiers would appear when the production of the corresponding noun is easier, to spread the information contained by the classifier and noun less densely over time. General classifiers can be applied to any noun and contain no special information content. Zhan and Levy find that speakers use specific classifiers more often in cases where the production of the corresponding noun is more difficult than when the production is easier; speakers do not avoid unexpected peaks in information content for their listeners, but instead maximize their ease of production. 
Similar to the original @levy2007, @zhan2018 focuses on information distribution at particular points in a sentence. By contrast, @jain2018 examine word order across spoken sentences in Hindi, a freer word order language than English, and find that information density has no significant effect on word order.

Recently, @yu2016 developed a more direct test of the Uniform Information Density hypothesis, applying the logic used by @genzel2002 to look at the distribution of information *within* individual sentences. **SOME HIGHER LEVEL DESCRIPTION HERE, WE'll GET INTO THE DETAILS BELOW**

Because people process language incrementally--using the previous words in a sentence to predict the words that will come next, the amount of information that a word contains when seen in isolation should increase over the course of a sentence. Analyzing a large corpus of written English, they find a different pattern: Entropy increases over the first few words of an utterance and then remains constant until the final word where it again jumps up (see Figure \ref{fig:our_replication}). @yu2016 conclude that the Uniform Information Density hypothesis must not hold for medial words in a sentence.

We extend and generalize @yu2016 in two ways: we confirm that this same pattern is found in spoken English--in both adult and child speakers. We then examine entropy curves cross-linguistically, finding a diversity of shapes across the world's languages. Finally, we show that entropy curves are predictable from the structure of individual languages, namely word order. Taken together, our results suggest a refinement of the Uniform information density hypothesis: Speakers may choose to order words in order to preserve uniform uniformation, but they must do so under prior constraints on word order imposed by the language they speak.

@@

@yu2016 challenges the UID hypothesis through examining an entropy measure across sentence positions within the text portion of the English-language British National Corpus (BNC, CITE). They partition the corpus by sentence length in number of words. For each word position $X$ of sentences of length $k$, they define $w$ as a unique word occurring in position $X$. They define $p(w)$ as the number of times word $w$ occurs in position $X$ divided by the number of total words that occur in position $X$ i.e. the number of sentences of length $k$. Then $p(w)$ is the probability of obtaining word $w$ by choosing a word at random in position $X$ in sentences of length $k$.

@@

We used the Brown and Providence English corpora from CHILDES. The Brown corpus contains individual recordings of conversations between three children between 1.5 and 6-years-old and their families in their homes. The Providence corpus recorded interactions between children between 1 and 3 years old and their parents in the home. We divided each corpus by speaker into child and non-child categories. We further divided the corpora by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position.

In the English CHILDES corpora. The entropy curves capture individual variation across positions in utterances of the same length. This allows us to directly observe and judge the amount of variation in words that appear in an individual position of a sentence. For speech data, which for the corpora in the CHILDES database consists of short and often disconnected utterances across hours of recordings, the unigram entropy measure is unaffected by context or lack thereof in utterances by the adults and children in the corpora. We can directly compare any two positions within utterances to determine the amount of uncertainty, and therefore information, on average contained by words within that position of utterances. We are applying the same approach as in @genzel2002, but within sentences instead of across sentences.

Plots for the entropy distributions are below.

```{r brown_PE, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Brown corpus entropy"}
img <- png::readPNG("figs/positional_entropy_brown.png")
grid::grid.raster(img)
```

@@

```{r shiro_PE, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Shiro corpus entropy"}
img <- png::readPNG("figs/German_unigram_entropies_with_stemming.png")
grid::grid.raster(img)
```

>>>>

abstract: >
    We provide evidence against the popular Uniform Information Density hypothesis (Levy & Jaeger, 2007) which proposes that information is transmitted at a constant rate close to channel capacity in human communication. Using a method based on the original Genzel & Charniak (2002) entropy measure, we construct a word-level model for entropy applicable to both spoken and written corpora. We apply this model to corpora from Wikipedia in well over a hundred languages. We find that the Uniform Information Density hypothesis does not predict the outcome of our word-level entropy model, but also that the by-word entropy distribution of a language is related to the typological features of the language. We use this evidence to suggest that people do not communicate information at a uniform rate, but that information distribution varies from language to language based on phonogical, morphological and syntactic features.

@@

# Introduction

@@

<!-- **Evidence for UID here. Maybe see if you can present this work at a slightly higher level** -->
The original evidence in @levy2007 finds that the insertion of complementizers in relative clauses in English corresponds to where neighboring words have high information content. Similarly, @frank2008speaking argues that contradictions in English such as "you're" do not occur when neighboring words are highly informative. The evidence in favor of UID largely been situation-specific and English-language driven, while the hypothesis itself has been applied broadly over the past decade. Applications include determining whether linguistic alignment takes place [@jaeger2013], Zipfian word length distributions [@piantadosi2011], communication efficiency [@mahowald2013], dialogue and turn-taking [@xu2018] and the significance of ambiguity in language [@piantadosi2012], among other research.

<!-- **Evidence against UID here. Again, can you present this at a higher level?** -->
However, other recent work has contradicted the UID hypothesis. Similar to the original @levy2007, @zhan2018 focuses on information distribution at particular points in sentences. @zhan2018 finds that more information-rich classifiers in Mandarin Chinese are produced when production of the neighboring noun is difficult, not when the information content is high. @jain2018 examine word order across spoken sentences in Hindi, a freer word order language than English, and find that information density has no significant effect on word order.

Recently, @yu2016 developed a more direct test of the Uniform Information Density hypothesis, applying the logic used by @genzel2002 to look at the distribution of information *within* individual sentences. <!-- **SOME HIGHER LEVEL DESCRIPTION HERE, WE'll GET INTO THE DETAILS BELOW** -->Because people process language incrementally--using the previous words in a sentence to predict the words that will come next, the amount of information that a word contains when seen in isolation should increase over the course of a sentence. Analyzing a large corpus of written English, they find a different pattern: Entropy increases over the first few words of an utterance and then remains constant until the final word where it again jumps up (see Figure \ref{fig:our_replication}). @yu2016 conclude that the Uniform Information Density hypothesis must not hold for medial words in a sentence.

We extend and generalize @yu2016 in three ways: we confirm that this same pattern is found in spoken English--in both adult and child speakers. We then examine entropy curves cross-linguistically, finding a diversity of shapes across the world's languages. Finally, we show that entropy curves are predictable from the structure of individual languages, namely word order. Taken together, our results suggest a refinement of the Uniform Information Density hypothesis: Speakers may choose to order words in order to preserve uniform information, but they must do so under prior constraints on word order imposed by the language they speak.

@@

@yu2016 challenges the UID hypothesis through examining an entropy measure across sentence positions within the text portion of the English-language British National Corpus (BNC) @clear1993british. They partition the corpus by sentence length in number of words. For each word position $X$ of sentences of length $k$, they define $w$ as a unique word occurring in position $X$. They define $p(w)$ as the number of times word $w$ occurs in position $X$ divided by the number of total words that occur in position $X$ i.e. the number of sentences of length $k$. Then $p(w)$ is the probability of obtaining word $w$ by choosing a word at random in position $X$ in sentences of length $k$.

@@

We used the Providence English corpds from CHILDES. The Providence corpus recorded interactions between children between 1 and 3 years old and their parents in the home. We divided the corpus by speaker into child and non-child categories. We further divided the corpus by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position.

The entropy curves capture individual variation across positions in utterances of the same length. This allows us to directly observe and judge the amount of variation in words that appear in an individual position of a sentence. For speech data, which for the corpora in the CHILDES database consists of short and often disconnected utterances across hours of recordings, the unigram entropy measure is unaffected by context or lack thereof in utterances by the adults and children in the corpora. We can directly compare any two positions within utterances to determine the amount of uncertainty, and therefore information, on average contained by words within that position of utterances. We are applying the same approach as in @genzel2002, but within sentences instead of across sentences.

@@

```{r shiro_PE, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Shiro corpus entropy"}
img <- png::readPNG("figs/Spanish_unigram_entropies_with_stemming.png")
grid::grid.raster(img)
```

### 2019-01-29 cogsci/position-info.tex
cogsci edits

\begin{abstract}
We provide evidence against the popular Uniform Information Density
hypothesis (Levy \& Jaeger, 2007) which proposes that information is
transmitted at a constant rate close to channel capacity in human
communication. Using a method based on the original Genzel \& Charniak
(2002) entropy measure, we construct a word-level model for entropy
applicable to both spoken and written corpora. We apply this model to
corpora from Wikipedia in well over a hundred languages. We find that
not only is the Uniform Information Density hypothesis prediction wrong,
but also that the by-word entropy distribution of a language is related
to the typological features of the language. We use this evidence to
suggest that people do not communicate information at a uniform rate,
but that information distribution varies from language to language based
on phonogical, morphological and syntactic features.

@@

Perhaps the most important reason people talk and write to one another
is to give information. From Shannon (1948), we know that when
information is being communicated, the rate of information transmission
should be constant and as close as possible to the capacity of the
communication channel to optimally transmit the information.
({\textbf{???}}) introduce the \emph{uniform information density} (UID)
hypothesis, arguing that people unconsciously structure their speech and
writing to communicate information at a constant, optimal rate.
({\textbf{???}}) argue that speakers and writers should attempt to
communicate information as evenly as possible and as close to the
channel capacity as possible. Their evidence concerns the use or lack of
use of ``that''-complementizers in introducing English relative clauses.
When the word preceding the relative clause or the initial word of the
relative clause has high information content, then the authors argue
that speakers are more likely to use the complementizer. The authors use
adult-adult conversations from the Penn Treebank corpus.

UID has been applied broadly over the past decade, to determining
whether linguistic alignment takes place (Jaeger \& Snider, 2013),
Zipfian word length distributions (Piantadosi, Tily, \& Gibson, 2011),
communication efficiency (Mahowald, Fedorenko, Piantadosi, \& Gibson,
2013), dialogue and turn-taking (Xu \& Reitter, 2018) and the
significance of ambiguity in language (Piantadosi, Tily, \& Gibson,
2012), among other research. However, other recent work has contradicted
the UID hypothesis. Zhan \& Levy (2018) study Mandarin Chinese
classifier use for specific and general Mandarin classifiers. Specific
classifiers are specific to certain nouns, and UID would predict that
specific classifiers would appear when the production of the
corresponding noun is easier, to spread the information contained by the
classifier and noun less densely over time. General classifiers can be
applied to any noun and contain no special information content. Zhan and
Levy find that speakers use specific classifiers more often in cases
where the production of the corresponding noun is more difficult than
when the production is easier; speakers do not avoid unexpected peaks in
information content for their listeners, but instead maximize their ease
of production.

Similar to the original ({\textbf{???}}), Zhan \& Levy (2018) focuses on
information distribution at particular points in a sentence. By
contrast, Jain, Singh, Ranjan, Rajkumar, \& Agarwal (2018) examine word
order across spoken sentences in Hindi, a freer word order language than
English, and find that information density has no significant effect on
word order. For this paper, we focus on the sentence level instead of
specific points, following a method described in Yu, Cong, Liang, \& Liu
(2016).

Yu et al. (2016) challenges the UID hypothesis through examining an
entropy measure across sentence positions within the text portion of the
English-language British National Corpus (BNC, CITE). They partition the
corpus by sentence length in number of words. For each word position
\(X\) of sentences of length \(k\), they define \(w\) as a unique word
occurring in position \(X\). They define \(p(w)\) as the number of times
word \(w\) occurs in position \(X\) divided by the number of total words
that occur in position \(X\) i.e.~the number of sentences of length
\(k\). Then \(p(w)\) is the probability of obtaining word \(w\) by
choosing a word at random in position \(X\) in sentences of length
\(k\).

@@

The entropy curve is a consequence of the information-theoretic rate of
information transfer in a language, where information is defined as a
reduction in uncertainty. Thus the more entropy at a word position in a
sentence (Yu et al., 2016) or a sentence index in a text (Genzel \&
Charniak, 2002), the more information is on average contained around
that position. Let us assume that the UID perspective is correct. Then
we expect that the entropy curve for every language should be close to
an affine, linear function with some noise. Entropy should monotonically
and uniformly increase at all word positions across utterances on
average. We will find a contradiction with this claim through examining
the average entropy at each position of a sentence for both speech and
text data.

{[}Put in an illustration of what UID predicts?{]}

\hypertarget{spoken-data}{%
\section{Spoken data}\label{spoken-data}}

The UID hypothesis predicts that information transmission rate will tend
towards uniformity in both speech and text. We begin by examining speech
to determine if we obtain the entropy curve shape we expect for spoken
communication. We begin with the same source as ({\textbf{???}}) and
Jaeger (2010), the Switchboard corpus of adult telephone conversations.
We also examine child-adult conversations in the CHILDES TalkBank
(Brown, 1973; MacWhinney, 2014) corpora database of spoken adult-child
conversations in multiple languages. Children are not fully developed
speakers, so we want to compare the entropy curve we obtain by computing
over the utterances in the CHILDES corpora to the utterances in the
adult-adult Switchboard corpus.

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

@@

We used the Brown and Providence English corpora from CHILDES. The Brown
corpus contains individual recordings of conversations between three
children between 1.5 and 6-years-old and their families in their homes.
The Providence corpus recorded interactions between children between 1
and 3 years old and their parents in the home. We divided each corpus by
speaker into child and non-child categories. We further divided the
corpora by utterance length, so that all sentences of length \(k\) (e.g.
\(6\)) were grouped together. Finally, within each utterance length, we
computed the unigram entropy measure for each position.

In the English CHILDES corpora. The entropy curves capture individual
variation across positions in utterances of the same length. This allows
us to directly observe and judge the amount of variation in words that
appear in an individual position of a sentence. For speech data, which
for the corpora in the CHILDES database consists of short and often
disconnected utterances across hours of recordings, the unigram entropy
measure is unaffected by context or lack thereof in utterances by the
adults and children in the corpora. We can directly compare any two
positions within utterances to determine the amount of uncertainty, and
therefore information, on average contained by words within that
position of utterances. We are applying the same approach as in Genzel
\& Charniak (2002), but within sentences instead of across sentences.

Plots for the entropy distributions are below.

{\centering \includegraphics{figs/brown_PE-1}

\caption[Brown corpus entropy]{Brown corpus entropy}\label{fig:brown_PE}
\end{figure*}
\end{CodeChunk}

@@

\hypertarget{results-analysis}{%
\subsection{Results \& Analysis}\label{results-analysis}}

@@

\hypertarget{written-data}{%
\section{Written data}\label{written-data}}

@@

\hypertarget{methods-1}{%
\subsection{Methods}\label{methods-1}}

@@

\hypertarget{results-and-analysis}{%
\subsection{Results and Analysis}\label{results-and-analysis}}

@@

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}

\noindent

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-brown1973}{}%
Brown, R. (1973). \emph{A first language: The early stages.} Harvard U.
Press.

\leavevmode\hypertarget{ref-genzel2002}{}%
Genzel, D., \& Charniak, E. (2002). Entropy rate constancy in text. In
\emph{Proceedings of the 40th annual meeting on association for
computational linguistics} (pp. 199--206). Association for Computational
Linguistics.

\leavevmode\hypertarget{ref-jaeger2010}{}%
Jaeger, T. F. (2010). Redundancy and reduction: Speakers manage
syntactic information density. \emph{Cognitive Psychology},
\emph{61}(1), 23--62.

\leavevmode\hypertarget{ref-jaeger2013}{}%
Jaeger, T. F., \& Snider, N. E. (2013). Alignment as a consequence of
expectation adaptation: Syntactic priming is affected by the prime's
prediction error given both prior and recent experience.
\emph{Cognition}, \emph{127}(1), 57--83.

\leavevmode\hypertarget{ref-jain2018}{}%
Jain, A., Singh, V., Ranjan, S., Rajkumar, R., \& Agarwal, S. (2018).
Uniform information density effects on syntactic choice in hindi. In
\emph{Proceedings of the workshop on linguistic complexity and natural
language processing} (pp. 38--48).

\leavevmode\hypertarget{ref-macwhinney2014}{}%
MacWhinney, B. (2014). \emph{The childes project: Tools for analyzing
talk, volume ii: The database}. Psychology Press.

\leavevmode\hypertarget{ref-mahowald2013}{}%
Mahowald, K., Fedorenko, E., Piantadosi, S. T., \& Gibson, E. (2013).
Info/information theory: Speakers choose shorter words in predictive
contexts. \emph{Cognition}, \emph{126}(2), 313--318.

\leavevmode\hypertarget{ref-piantadosi2011}{}%
Piantadosi, S. T., Tily, H., \& Gibson, E. (2011). Word lengths are
optimized for efficient communication. \emph{Proceedings of the National
Academy of Sciences}, \emph{108}(9), 3526--3529.

\leavevmode\hypertarget{ref-piantadosi2012}{}%
Piantadosi, S. T., Tily, H., \& Gibson, E. (2012). The communicative
function of ambiguity in language. \emph{Cognition}, \emph{122}(3),
280--291.

\leavevmode\hypertarget{ref-shannon1948}{}%
Shannon, C. E. (1948). A mathematical theory of communication.
\emph{Bell System Technical Journal}, \emph{27}(3), 379--423.

\leavevmode\hypertarget{ref-xu2018}{}%
Xu, Y., \& Reitter, D. (2018). Information density converges in
dialogue: Towards an information-theoretic model. \emph{Cognition},
\emph{170}, 147--163.

\leavevmode\hypertarget{ref-yu2016}{}%
Yu, S., Cong, J., Liang, J., \& Liu, H. (2016). The distribution of
information content in english sentences. \emph{arXiv Preprint
arXiv:1609.07681}.

\leavevmode\hypertarget{ref-zhan2018}{}%
Zhan, M., \& Levy, R. (2018). Comparing theories of speaker choice using
a model of classifier production in mandarin chinese. In
\emph{Proceedings of the 2018 conference of the north american chapter
of the association for computational linguistics: Human language
technologies, volume 1 (long papers)} (Vol. 1, pp. 1997--2005).

>>>>

\begin{abstract}
We provide evidence against the popular Uniform Information Density
hypothesis (Levy \& Jaeger, 2007) which proposes that information is
transmitted at a constant rate close to channel capacity in human
communication. Using a method based on the original Genzel \& Charniak
(2002) entropy measure, we construct a word-level model for entropy
applicable to both spoken and written corpora. We apply this model to
corpora from Wikipedia in well over a hundred languages. We find that
the Uniform Information Density hypothesis does not predict the outcome
of our word-level entropy model, but also that the by-word entropy
distribution of a language is related to the typological features of the
language. We use this evidence to suggest that people do not communicate
information at a uniform rate, but that information distribution varies
from language to language based on phonogical, morphological and
syntactic features.

@@

\section{Introduction}\label{introduction}

Over 7,000 languages are spoken around the modern world (Simons \&
Fenning, 2018). These language vary along many dimensions, but all share
a core goal: communicating information. If speakers and writers of these
languages act near-optimally to achieve their communicative goals,
regularities of use across these diverse languages can be explained by a
rational theory of communication (Anderson, 1991). Information theory, a
mathematical framework developed by Shannon (1948) to describe the
transmission and decoding of signals, has been a unifying language for
the recent development of such theories in human and machine language
processing (Jelinek, 1976; R. P. Levy \& Jaeger, 2007).

These theories model the process of communication as transmission of
information over a noisy channel. The producer begins with an intended
meaning, packages this meaning into a linguistic format, and then sends
it to the receiver over a communcative channel. The receiver must then
decode from the signal they receive on their end of the chanel the
producer's intended meaning. The problem is that the channel is noisy,
and sometimes the signal can get corrupted (e.g.~the producer can
misspeak, or the receiver can mishear). In order to maximize the
probability that the correct meaning is transmitted, these theories
predict that producers should choose linguistic messages that keep the
rate of information across words constant. The intuition is that if the
receiver misperceives a word, and that word contains most of the
information in the sentence, then the communication will have failed.
Because producers cannot predict which word a speaker will mishear,
their best strategy is spread the information evenly across all of the
words in a sentence, i.e.~maintain \emph{uniform information density}
(Genzel \& Charniak, 2002; R. P. Levy \& Jaeger, 2007).

The original evidence in R. P. Levy \& Jaeger (2007) finds that the
insertion of complementizers in relative clauses in English corresponds
to where neighboring words have high information content. Similarly,
Frank \& Jaeger (2008) argues that contradictions in English such as
``you're'' do not occur when neighboring words are highly informative.
The evidence in favor of UID largely been situation-specific and
English-language driven, while the hypothesis itself has been applied
broadly over the past decade. Applications include determining whether
linguistic alignment takes place (Jaeger \& Snider, 2013), Zipfian word
length distributions (Piantadosi, Tily, \& Gibson, 2011), communication
efficiency (Mahowald, Fedorenko, Piantadosi, \& Gibson, 2013), dialogue
and turn-taking (Xu \& Reitter, 2018) and the significance of ambiguity
in language (Piantadosi, Tily, \& Gibson, 2012), among other research.

However, other recent work has contradicted the UID hypothesis. Similar
to the original R. P. Levy \& Jaeger (2007), Zhan \& Levy (2018) focuses
on information distribution at particular points in sentences. Zhan \&
Levy (2018) finds that more information-rich classifiers in Mandarin
Chinese are produced when production of the neighboring noun is
difficult, not when the information content is high. On a sentential
level, Jain, Singh, Ranjan, Rajkumar, \& Agarwal (2018) examine word
order across spoken sentences in Hindi, a freer word order language than
English, and find that information density has no significant effect on
word order.

Recently, Yu, Cong, Liang, \& Liu (2016) developed a more direct test of
the Uniform Information Density hypothesis, applying the logic used by
Genzel \& Charniak (2002) to look at the distribution of information
\emph{within} individual sentences. Because people process language
incrementally--using the previous words in a sentence to predict the
words that will come next, the amount of information that a word
contains when seen in isolation should increase over the course of a
sentence. Analyzing a large corpus of written English, they find a
different pattern: Entropy increases over the first few words of an
utterance and then remains constant until the final word where it again
jumps up (see Figure \ref{fig:our_replication}). Yu et al. (2016)
conclude that the Uniform Information Density hypothesis must not hold
for medial words in a sentence.

We extend and generalize Yu et al. (2016) in three ways: we confirm that
this same pattern is found in spoken English--in both adult and child
speakers. We then examine entropy curves cross-linguistically, finding a
diversity of shapes across the world's languages. Finally, we show that
entropy curves are predictable from the structure of individual
languages, namely word order. Taken together, our results suggest a
refinement of the Uniform Information Density hypothesis: Speakers may
choose to order words in order to preserve uniform information, but they
must do so under prior constraints on word order imposed by the language
they speak.

The UID hypothesis predicts that information transmission rate will tend
towards uniformity in both speech and text. We begin by examining speech
to determine if we obtain the entropy curve shape we expect for spoken
communication. We begin with the same source as R. P. Levy \& Jaeger
(2007) and Jaeger (2010), the Switchboard corpus of adult telephone
conversations. We also examine child-adult conversations in the CHILDES
TalkBank (Brown, 1973; MacWhinney, 2014) corpora database of spoken
adult-child conversations in multiple languages. Children are not fully
developed speakers, so we want to compare the entropy curve we obtain by
computing over the utterances in the CHILDES corpora to the utterances
in the adult-adult Switchboard corpus.

\subsection{Methods}\label{methods}

Yu et al. (2016) challenges the UID hypothesis through examining an
entropy measure across sentence positions within the text portion of the
English-language British National Corpus (BNC) Clear (1993). They
partition the corpus by sentence length in number of words. For each
word position \(X\) of sentences of length \(k\), they define \(w\) as a
unique word occurring in position \(X\). They define \(p(w)\) as the
number of times word \(w\) occurs in position \(X\) divided by the
number of total words that occur in position \(X\) i.e.~the number of
sentences of length \(k\). Then \(p(w)\) is the probability of obtaining
word \(w\) by choosing a word at random in position \(X\) in sentences
of length \(k\).

@@

@@

We used the Providence English corpds from CHILDES. The Providence
corpus recorded interactions between children between 1 and 3 years old
and their parents in the home. We divided the corpus by speaker into
child and non-child categories. We further divided the corpus by
utterance length, so that all sentences of length \(k\) (e.g. \(6\))
were grouped together. Finally, within each utterance length, we
computed the unigram entropy measure for each position.

The entropy curves capture individual variation across positions in
utterances of the same length. This allows us to directly observe and
judge the amount of variation in words that appear in an individual
position of a sentence. For speech data, which for the corpora in the
CHILDES database consists of short and often disconnected utterances
across hours of recordings, the unigram entropy measure is unaffected by
context or lack thereof in utterances by the adults and children in the
corpora. We can directly compare any two positions within utterances to
determine the amount of uncertainty, and therefore information, on
average contained by words within that position of utterances. We are
applying the same approach as in Genzel \& Charniak (2002), but within
sentences instead of across sentences.

@@

\subsection{Results \& Analysis}\label{results-analysis}

@@

\section{Written data}\label{written-data}

@@

\subsection{Methods}\label{methods-1}

@@

\subsection{Results and Analysis}\label{results-and-analysis}

@@

\section{Conclusions}\label{conclusions}

@@

\section{Acknowledgements}\label{acknowledgements}

@@

\section{References}\label{references}

\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent

\hypertarget{refs}{}
\hypertarget{ref-anderson1991}{}
Anderson, J. R. (1991). The adaptive nature of human categorization.
\emph{Psychological Review}, \emph{98}(3), 409.

\hypertarget{ref-brown1973}{}
Brown, R. (1973). \emph{A first language: The early stages.} Harvard U.
Press.

\hypertarget{ref-clear1993british}{}
Clear, J. H. (1993). The british national corpus. \emph{The Digital
World}, 163--187.

\hypertarget{ref-frank2008speaking}{}
Frank, A. F., \& Jaeger, T. F. (2008). Speaking rationally: Uniform
information density as an optimal strategy for language production. In
\emph{Proceedings of the annual meeting of the cognitive science
society} (Vol. 30).

\hypertarget{ref-genzel2002}{}
Genzel, D., \& Charniak, E. (2002). Entropy rate constancy in text. In
\emph{Proceedings of the 40th annual meeting on association for
computational linguistics} (pp. 199--206). Association for Computational
Linguistics.

\hypertarget{ref-jaeger2010}{}
Jaeger, T. F. (2010). Redundancy and reduction: Speakers manage
syntactic information density. \emph{Cognitive Psychology},
\emph{61}(1), 23--62.

\hypertarget{ref-jaeger2013}{}
Jaeger, T. F., \& Snider, N. E. (2013). Alignment as a consequence of
expectation adaptation: Syntactic priming is affected by the prime's
prediction error given both prior and recent experience.
\emph{Cognition}, \emph{127}(1), 57--83.

\hypertarget{ref-jain2018}{}
Jain, A., Singh, V., Ranjan, S., Rajkumar, R., \& Agarwal, S. (2018).
Uniform information density effects on syntactic choice in hindi. In
\emph{Proceedings of the workshop on linguistic complexity and natural
language processing} (pp. 38--48).

\hypertarget{ref-jelinek1976}{}
Jelinek, F. (1976). Continuous speech recognition by statistical
methods. \emph{Proceedings of the IEEE}, \emph{64}(4), 532--556.

\hypertarget{ref-levy2007}{}
Levy, R. P., \& Jaeger, T. F. (2007). Speakers optimize information
density through syntactic reduction. In \emph{Advances in neural
information processing systems} (pp. 849--856).

\hypertarget{ref-macwhinney2014}{}
MacWhinney, B. (2014). \emph{The childes project: Tools for analyzing
talk, volume ii: The database}. Psychology Press.

\hypertarget{ref-mahowald2013}{}
Mahowald, K., Fedorenko, E., Piantadosi, S. T., \& Gibson, E. (2013).
Info/information theory: Speakers choose shorter words in predictive
contexts. \emph{Cognition}, \emph{126}(2), 313--318.

\hypertarget{ref-piantadosi2011}{}
Piantadosi, S. T., Tily, H., \& Gibson, E. (2011). Word lengths are
optimized for efficient communication. \emph{Proceedings of the National
Academy of Sciences}, \emph{108}(9), 3526--3529.

\hypertarget{ref-piantadosi2012}{}
Piantadosi, S. T., Tily, H., \& Gibson, E. (2012). The communicative
function of ambiguity in language. \emph{Cognition}, \emph{122}(3),
280--291.

\hypertarget{ref-shannon1948}{}
Shannon, C. E. (1948). A mathematical theory of communication.
\emph{Bell System Technical Journal}, \emph{27}(3), 379--423.

\hypertarget{ref-simons2018}{}
Simons, G. F., \& Fenning, C. D. (Eds.). (2018). \emph{Ethnologue:
Languages of the world, 21st edition}. Dallas, Texas: SIL International.

\hypertarget{ref-xu2018}{}
Xu, Y., \& Reitter, D. (2018). Information density converges in
dialogue: Towards an information-theoretic model. \emph{Cognition},
\emph{170}, 147--163.

\hypertarget{ref-yu2016}{}
Yu, S., Cong, J., Liang, J., \& Liu, H. (2016). The distribution of
information content in english sentences. \emph{arXiv Preprint
arXiv:1609.07681}.

\hypertarget{ref-zhan2018}{}
Zhan, M., \& Levy, R. (2018). Comparing theories of speaker choice using
a model of classifier production in mandarin chinese. In
\emph{Proceedings of the 2018 conference of the north american chapter
of the association for computational linguistics: Human language
technologies, volume 1 (long papers)} (Vol. 1, pp. 1997--2005).
